\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-12-01 papers/jss/article.Rnw
Add a missing article to Jeroen's nice rewording of this section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@923 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Protocol Buffers are used extensively at Google for almost all
RPC protocols, and to store structured information on a variety of
persistent storage systems \citep{dean2009designs}. Since the 
initial release in 2010, hundreds of Google's statisticians and
software engineers use the \pkg{RProtoBuf} package on daily basis 
to interact with these systems from within \proglang{R}.
The current section illustrates the power of Protocol Buffers to
collect and manage large structured data in one language 
before analyzing it in \proglang{R}. Our example uses MapReduce
\citep{dean2008mapreduce}, which has emerged in the last
decade as a popular design pattern to facilitate parallel 
processing of big data using distributed computing clusters.

>>>>

Protocol Buffers are used extensively at Google for almost all
RPC protocols, and to store structured information on a variety of
persistent storage systems \citep{dean2009designs}. Since the
initial release in 2010, hundreds of Google's statisticians and
software engineers use the \pkg{RProtoBuf} package on a daily basis
to interact with these systems from within \proglang{R}.
The current section illustrates the power of Protocol Buffers to
collect and manage large structured data in one language 
before analyzing it in \proglang{R}. Our example uses MapReduce
\citep{dean2008mapreduce}, which has emerged in the last
decade as a popular design pattern to facilitate parallel 
processing of big data using distributed computing clusters.
